Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-16 paper.tex
More minor changes.

%The reason of combine VeRi-776 dataset into training set is that
Since the orientation label is only available in VeRi-776,
for training the full MTML model including orientation supervisory signal,
we did the second experiment which included both this database plus CityFlow.
%
Table \ref{T:cf_veri_res} shows that:
(1) By adding VeRi-776 training data,
with MTML-S, MTML-G and MTML-SG,
we all obtain a better mAP and CMC performance on CityFlow
than the model which was only trained on CityFlow.
Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
than the model only training on VeRi-776. We suspect this is due to training
for a shorter period of time, as this experiment ran for only 100 epochs, compared to 150.
(2) By adding orientation branch, the MLTML-OSG model totalling 4 branches,
we obtain the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
CityFlow respectively.
This shows that our method of mutual learning between the orientation branch supervised by orientation labels and the other branches supervised by ID label is effective.

>>>>

%The reason of combine VeRi-776 dataset into training set is that
Since the orientation label is only available in VeRi-776,
for training the full MTML model including orientation supervisory signal,
we did the second experiment which included both this database plus CityFlow.
%
Table \ref{T:cf_veri_res} shows that:
(1) By adding VeRi-776 training data,
with MTML-S, MTML-G and MTML-SG,
we all obtain a better mAP and CMC performance on CityFlow
than the model which was only trained on CityFlow.
Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
than the model only training on VeRi-776. We suspect this is due to training
for a shorter period of time, as this experiment ran for only 100 epochs, compared to 150.
(2) By adding the orientation branch, for the MLTML-OSG model,
we obtain the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
CityFlow respectively. This is improved to {66.4\%} and {29.2\%} with reranking.
This shows that our method of mutual learning between the orientation branch supervised by orientation labels and the other branches supervised by ID label is effective.
